\thispagestyle{empty}
\afterpage{
    \newgeometry{top = 0.7 in,
     bottom = 0.7 in,
     left = 1.13 in,
     right = 1.13 in,}
    
    \begin{center}
        \textbf{Acknowledgements}
    \end{center}
    
    % \vspace{0.25 cm}
    
    \begin{center}
    \sectionlinetwo{black}{88}
    \end{center}

    % \vspace{0.15 cm}
    
    \paragraph{} I really do not know how to pull this off, but firstly this one goes to my parents and my brothers. If I reached my goals and fullfilled my dreams, today, it's only because of your massive and valuable sacrifices which one day I \textit{promise} to pay back. These have been 2 tough years, but just know I love you from the bottom of my heart and that this achievement is dedicated to you, hoping I succeeded in making you proud.
    
    \paragraph{} I would like to thank Professor Irene Amerini for always believing in me from day one, along with the whole crew at Smart-I, which gave me the incredible opportunity of developing this thesis in the most friendly environment I could have ever found myself in.
    
    \paragraph{}Thank you Giancarlo for sharing this stage throughout all these years, between our own first apartment and study life. Lord knows how many times you were standing at my door, silently, for minutes, hoping I'd notice you so that you could start brainstorming me with AI-related questions. Haha.. miss those days, man. Thank you for making this journey feel like still being at home.
    
    \paragraph{} Silvia, my bestie. We grew up together and yet you're still here for another milestone. As we always said during our years, we might not get in touch every single day, but knowing I have you by my side and viceversa is the best thing I could've asked for, because coming back to each other is always like we never left.
    
    \paragraph{} My appreciation extends to Gianluigi. Thank you for introducing me to the beauty of Rome, for all the late night beers underneath the Colosseum and for always being actively present when I didn't even ask for it. I'll make sure to keep your lessons in a safe place. You're the definition of a true brother. I love you, dawg.
    
    \paragraph{} To my 4 best mates, I'm grateful for every single one of you: Giuseppe, Domenico, Alessandro and Mattia. Thank you for being who you actually are and for always inspiring and encouraging me to reach my goals. A big round of applause also for my whole group of friends from my hometown. Coming back to you, guys, it's always so nice and distracting.
    
    \paragraph{} Lorenzo, my Roman best friend. Thank you for the endless car travels, the laughs and the precious advices. You're more than a simple University friend. Also, thanks to my wonderful colleagues and friends Emanuele, Claudio, Lorenzo, Giulio, Camilla and Jacopo. Martina, I deeply appreciate you for constantly supporting me during this final sprint. We both know that I probably wouldn't be here today if it wasn't for your immense help, so.. thank you.
    
    \paragraph{} I couldn't go without sharing a line of gratitude for my music. Thank you dear for speaking for me when I couldn't. A special mention goes to my musician friend Alex. Your music truly shaped who I actually am today, giving me a secure place to shelter when I needed it. Rome wasn't the same without your unique touch of sounds. This also extends to the whole Underscore server too, thank you guys. To all my family and to my gorgeous cousin Francy. To Antonella, because despite everything, you're still a wonderful friend to count on.
    
    \paragraph{} Lastly, but not least, this goes to my grandparents.\\I know they are proud of me, as I am of them too. I miss you, loves, wherever you are.
    
    \vspace{0.25 cm}
    
    \begin{center}
        \textit{Gianmarco Scarano, January 2025.}
    \end{center}
    
    \begin{center}
        \sectionlinetwo{black}{88}
    \end{center}
    
    \clearpage
    \restoregeometry
}
